A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-07-15 src/paper.tex
Second screen devices

The second screen devices are used to interact with the content being watched in the TV terminal.

>>>>

The second screen devices are clients that communicate with the web application in order to provide interactive capabilities with the content being watched in the TV terminal. The communication between second screen clients and the web application is made through HTTP requests to the web services. Basically, there are two types of communication between clients and the web application: retrieval the content from the web server and transmission of the captured interactions to the web server.

The content presented on the second screen client, which is related to the TV content, is retrieved from the web server and it is formated to be shown on a specially designed native application.
